---
title: "Crinier_2020_Human_BM_NK_preprocessing"
author: "Dillon Corvino"
date: "11/08/2021"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: united
    highlight: tango
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

Built with R version `r getRversion()`

## Setup {.tabset}

### Dataset information
```{r Dataset_Info}




```

### Environment
```{r setup}

knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,  
  eval = TRUE, 
  tidy = TRUE
)

knitr::opts_knit$set(
  root.dir = "../"
)


# Environment Set up
rm(list = ls()) #Clean workspace
cat("\014")     #Clean Console
gc() # Free memory

# Establish working directory
library("rstudioapi")

# Set working directory to source file location
setwd(dirname(getActiveDocumentContext()$path))
setwd("..")

# Load packages
source("R/Load_packages.R", local = knitr::knit_global())

# Create output directories & load custom functions & colour scheme
source("R/Setup.R", local = knitr::knit_global())

long.compute <- FALSE
quick.load <- TRUE

```

### Read and format dataset
```{r reading_data}

if(long.compute){
  # List files 
  data.list <- list.files("Data/GSE159624_RAW/", pattern = ".csv")
  
  
  ############################
  # Read in sample data
  ############################
  
  # Create name variable
  file.names <- gsub("_normalized.csv", "", data.list)
  file.names <- gsub("GSM([0-9]+)_", "", file.names)
  file.names
  
  
  
  
  # Read in samples
  for (i in seq_along(data.list)){
    assign(file.names[i], read.csv(paste0("Data/GSE159624_RAW/", data.list[i])))
  }
  
  
  
  
  # Annotate the cell ids so can be identified later
  for(i in 1:8){
    
    AML <- eval(parse(text = paste0("AML_donor", i)))
    Healthy <- eval(parse(text = paste0("Healthy_donor", i)))
    
    
    
    colnames(AML) <- paste0(colnames(AML), "_AML_", i)
    colnames(Healthy) <- paste0(colnames(Healthy), "_Healthy_", i)
    
    colnames(AML)[1] <- "GeneID"
    colnames(Healthy)[1] <- "GeneID"
    
    assign(paste0("AML_donor", i), AML)
    assign(paste0("Healthy_donor", i), Healthy)
    
  }
  
  
  Healthy_donor1$GeneID
  
  ########################################
  # Merge data by organ of origin
  ########################################
  
  # Dplyr doesnt allow merge by rowname. so have to make it a variable and then return the variable
  
  healthy.dataset <- 
    full_join(Healthy_donor1, Healthy_donor2,  by = "GeneID") %>%
    full_join(Healthy_donor3,  by = "GeneID") %>%
    full_join(Healthy_donor4,  by = "GeneID") %>%
    full_join(Healthy_donor5,  by = "GeneID") %>%
    full_join(Healthy_donor6,  by = "GeneID") %>%
    full_join(Healthy_donor7,  by = "GeneID") %>%
    full_join(Healthy_donor8,  by = "GeneID") %>%
    arrange(desc = TRUE) %>%
    column_to_rownames(var = "GeneID")
  
  
  
  
  AML.dataset <- 
    full_join(AML_donor1, AML_donor2,  by = "GeneID") %>%
    full_join(AML_donor3,  by = "GeneID") %>%
    full_join(AML_donor4,  by = "GeneID") %>%
    full_join(AML_donor5,  by = "GeneID") %>%
    full_join(AML_donor6,  by = "GeneID") %>%
    full_join(AML_donor7,  by = "GeneID") %>%
    full_join(AML_donor8,  by = "GeneID") %>%
    arrange(desc = TRUE) %>%
    column_to_rownames(var = "GeneID")
  
  
  
  
  
  
  
  # Checking all genes were merged 
  AML.geneIDs <- unique(c(as.character(AML_donor1$GeneID), 
                          as.character(AML_donor2$GeneID), 
                          as.character(AML_donor3$GeneID), 
                          as.character(AML_donor4$GeneID), 
                          as.character(AML_donor5$GeneID), 
                          as.character(AML_donor6$GeneID), 
                          as.character(AML_donor7$GeneID), 
                          as.character(AML_donor8$GeneID)))
  
  length(AML.geneIDs) == nrow(AML.dataset)
  
  # overview stats
  dim(healthy.dataset)
  dim(AML.dataset)
  
  #####################
  # Format dataframe
  #####################
  
  
  
  # Merge all data together
  Human.dataset <- merge(healthy.dataset, AML.dataset, 
                         by = "row.names", 
                         all = TRUE)
  
  # Annotate
  rownames(Human.dataset) <- Human.dataset$Row.names
  
  index.val <- grep("^Row.names$", colnames(Human.dataset))
  colnames(Human.dataset)[index.val]
  Human.dataset <- Human.dataset[,-index.val]
  
  
  
  
  # When a gene was detected in AML or Healthy but not the other there are now NA values for this entry in the other dataset cells
  # Remove NA values
  na.values <- is.na(Human.dataset)
  sum(na.values) # 14,8438,953
  
  # Assigning NA values as 0
  Human.dataset[na.values] <- 0
  
  # Checking NA values are removed
  sum(is.na(Human.dataset)) 
  
  dim(Human.dataset) # 18,232 genes and 39,628 cells 
  
  # Write data to file for easy use later
  write.csv(Human.dataset, "output/tables/Human_AML_and_Healthy.csv")
  saveRDS(Human.dataset, "Exported_RDS_files/Human_AML_and_Healthy.rds")
  saveRDS(AML.dataset, "Exported_RDS_files/Human_AML.rds")
  saveRDS(healthy.dataset, "Exported_RDS_files/Human_Healthy.rds")
  
  # remove large datafiles
  rm(Healthy_donor1, Healthy_donor2, Healthy_donor3, 
     Healthy_donor4, Healthy_donor5, Healthy_donor6, 
     Healthy_donor7, Healthy_donor8, 
     AML_donor1, AML_donor2, AML_donor3, AML_donor4, 
     AML_donor5, AML_donor6, AML_donor7, AML_donor8, AML, Healthy)
  
}


```

### Create seurat object
```{r create_Seurat_object}

# load data, create seurat object and calcualte mito percentage
load_data <- function(data.dir){
  data <- readRDS(data.dir)
  
  project.name <- gsub("Exported_RDS_files/", "", data.dir)
  project.name <- gsub(".rds", "", project.name)
  
  s.object <- CreateSeuratObject(counts = data,
                                 min.cells = 3, 
                                 project = project.name,
                                 min.genes = 200)
  
  s.object <- PercentageFeatureSet(s.object,
                                   pattern = "^MT-",
                                   col.name = "percent.mt")
  
  return(s.object)
}


healthy.dataset <- load_data("Exported_RDS_files/Human_Healthy.rds")

AML.dataset <- load_data("Exported_RDS_files/Human_AML.rds")


# Make a list of seurat objects
seurat.list <- c(healthy.dataset, AML.dataset)
names(seurat.list) <- c("Healthy", "AML")

saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list.rds")

# remove single seurat objects
rm(healthy.dataset, AML.dataset)

```



## QC and Filter {.tabset}

### QC & filter

```{r QC_and_filter}

if(long.compute){
  
  for(i in seq_along(seurat.list)){
    
    # Create output dir
    output.path <- paste0("output/QC/QC_", names(seurat.list)[i])
    
    
    if(!dir.exists(output.path)){
      dir.create(output.path, 
                 recursive = TRUE)}
    
    
    # Plot QC metrics 
    
    # nFeature & nCount & Mito
    print(
      VlnPlot(seurat.list[[i]], 
              features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), 
              pt.size = 0.1)
    )
    
    dev.copy(pdf,  paste0(output.path, "/QC_nFeature_nCount_RNA_percentMito.pdf"))
    dev.off()
    
    # Mito
    print(
      VlnPlot(seurat.list[[i]], 
              features = "percent.mt", 
              y.max = 20,
              pt.size = 0.1)
    )
    
    dev.copy(pdf,  paste0(output.path, "/QC_RNA_percentMito.pdf"))
    dev.off()
    
  }
  
  
  min.nFeature <- 400
  max.nFeature <- 3000
  max.nCount <- 3000
  max.Percent.Mt <- 5
  
  seurat.list <- lapply(seurat.list, 
                        FUN = subset,
                        subset = nFeature_RNA > min.nFeature & nFeature_RNA < max.nFeature & nCount_RNA < max.nCount & percent.mt < max.Percent.Mt)
  
  
  
  
  for(i in seq_along(seurat.list)){
    
    # output.dir
    output.path <- paste0("output/QC/QC_", names(seurat.list)[i])
    
    # After filtering
    print(
      VlnPlot(seurat.list[[i]],
              features = c("nFeature_RNA", "nCount_RNA", "percent.mt"),
              pt.size = 0.1)
    )
    
    dev.copy(pdf,  paste0(output.path, "/QC_nFeature_nCount_RNA_percentMito_Postfiltering.pdf"))
    dev.off()
    
  }
  

  # Post-filtering metrics
  seurat.list
  
  
  # Save filtered dataset
  saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list.rds")
  
  
}

```


## SCT normalise data

```{r SCT_normalisation}

if(long.compute){
# Normalise and scale with SCTransform 
seurat.list <- lapply(X = seurat.list, 
                      FUN = SCTransform, 
                      method = "glmGamPoi", 
                      vars.to.regress = "percent.mt", 
                      verbose = TRUE) 
  

 # Save normalised dataset
  saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list.rds")
  
}

```



## Combine patients {.tabset}

### Integrate data

```{r Integrate_patients}

if(long.compute){
  
  
  # Integrate datasets
  
  # Select features
  integration.features <- SelectIntegrationFeatures(object.list = seurat.list, 
                                                    nfeatures = 4000)
  
  # Prep dataset
  integrated.seurat <- PrepSCTIntegration(object.list = seurat.list, 
                                          anchor.features = integration.features)
  
  # perform PCA analysis
  integrated.seurat <- lapply(X = seurat.list, 
                              FUN = Seurat::RunPCA,
                              features = integration.features)
  
  
  # Find integration anchors
  integration.anchors <- FindIntegrationAnchors(object.list = integrated.seurat, 
                                                anchor.features = integration.features,
                                                normalization.method = 'SCT',
                                                reduction = "rpca", # rpca is more conservative, best for datasets which may not overlap alot
                                                k.anchor = 20) # increases strength of alignment
  
  # Integrate dataset
  integrated.seurat <- IntegrateData(anchorset = integration.anchors, 
                                     normalization.method = 'SCT')
  
  
  # Basic overview of data
  integrated.seurat # 30,04 genes and 5,060 cells 
  
  seurat.list[[1]] # 24,231 cells
  seurat.list[[2]] # 15,293 cells
  
  # Save files 
  saveRDS(integrated.seurat, file = "Exported_RDS_files/integrated_seurat.rds")
  
  # Remove unneeded data
  rm(integration.anchors, integration.features, features)
  
}


```




## Unbiased Clustering {.tabset}

### Clustering
```{r PCA_and_cluster_identification}

################################
# PCA and cluster identification
################################


# Set seed for reproducibility
set.seed(42)


# Calculate PCA
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::RunPCA,
                      npcs = 20, 
                      verbose = TRUE, 
                      rev.pca = TRUE,
                      seed.use = 42)

# Find neighbours
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::FindNeighbors,
                      dims = 1:20)

# Find clusters
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::FindClusters,
                      resolution = 0.1)



# Plot PCA
for(i in seq_along(seurat.list)){
  
  # Create output dir
  output.path <- paste0("output/figures/PCA_", names(seurat.list)[i])
  
  if(!dir.exists(output.path)){
    dir.create(output.path, 
               recursive = TRUE)}
  
  
  print(
    PCAPlot(seurat.list[[i]], 
            dims = c(1, 2),
            pt.size = 2, 
            group.by = "orig.ident")
  )
  
  dev.copy(pdf,  paste0(output.path, "/PCA_dim1_vs_2.pdf"))
  dev.off()
  
  
  print(
    PCAPlot(seurat.list[[i]], 
            dims = c(2, 3),
            pt.size = 2, 
            group.by = "orig.ident")
  )
  
  dev.copy(pdf,  paste0(output.path, "/PCA_dim2_vs_3.pdf"))
  dev.off()
  
  
  
}



#################################################################
# Determine statistically significant principal components
#################################################################

for(i in seq_along(seurat.list)){
  
  # get output.dir
  output.path <- paste0("output/figures/PCA_", names(seurat.list)[i])
  
  print(
    ElbowPlot(seurat.list[[i]],
              ndims = 20)
  )
  
  dev.copy(pdf,  paste0(output.path, "/PC_elbowplot.pdf"))
  dev.off()
}


# Not applicable for SCT-transformed 

if(long.compute){
  
  # NOTE: This process can take a long time for big datasets, comment out for
# expediency.  More approximate techniques such as those implemented in
# PCElbowPlot() can be used to reduce computation time
  
  
    seurat.list <- lapply(seurat.list, 
           FUN = Seurat::JackStraw,
           reduction = "pca", 
           dims = 50)
    
    seurat.list <- lapply(seurat.list, 
           FUN = Seurat::ScoreJackStraw,
           dims = 1:50)
    
    
      for(i in seq_along(seurat.list)){

      # get output.dir
  output.path <- paste0("output/figures/PCA_", names(seurat.list)[i])
  
  print(
    JackStrawPlot(seurat.list[[i]],
                  dims = 1:30)
  )
  
   dev.copy(pdf,  paste0(output.path, "/JackStrawPlot.pdf"))
  dev.off()
  
  }
}


```


### UMAP and tSNE dim Reduction
```{r Dim_reduction}

# Calculate tSNE
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::RunTSNE,
                      reduction = "pca",
                      dims = 1:20,
                      perplexity = 30,
                      method = "FIt-SNE",
                      seed.use = 42,
                      dim.embed = 2)

# Plot tSNE
for(i in seq_along(seurat.list)){
  
  # Create output dir
  output.path <- paste0("output/figures/tSNE_", names(seurat.list)[i])
  
  if(!dir.exists(output.path)){
    dir.create(output.path, 
               recursive = TRUE)}
  
  
  print(
    TSNEPlot(seurat.list[[i]], 
             group.by = "orig.ident")
  )
  
  dev.copy(pdf,  paste0(output.path, "/tSNE_orig_ident.pdf"))
  dev.off()
  
  
  print(
    TSNEPlot(seurat.list[[i]], 
             group.by = "seurat_clusters")
  )
  
  dev.copy(pdf,  paste0(output.path, "/tSNE_seurat_clusters.pdf"))
  dev.off()
  
  
}


 # Calculate UMAP
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::RunUMAP,
                      reduction = "pca",
                      dims = 1:20,
                      umap.method = "uwot", 
                      n.neighbors = 45, # 5 to 50 // 45
                      min.dist = 0.5, # Sensible values are in the range 0.001 to 0.5 // 0.5
                      seed.use = 42)

# Plot UMAP
for(i in seq_along(seurat.list)){
  
  # Create output dir
  output.path <- paste0("output/figures/UMAP_", names(seurat.list)[i])
  
  if(!dir.exists(output.path)){
    dir.create(output.path, 
               recursive = TRUE)}
  
  
  print(
    UMAPPlot(seurat.list[[i]], 
             group.by = "orig.ident")
  )
  
  dev.copy(pdf,  paste0(output.path, "/UMAP_orig_ident.pdf"))
  dev.off()
  
  
  print(
    UMAPPlot(seurat.list[[i]], 
             group.by = "seurat_clusters")
  )
  
  dev.copy(pdf,  paste0(output.path, "/UMAP_seurat_clusters.pdf"))
  dev.off()
  
  
}

# Save dataset with dim reduction
saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list.rds")

```



## Imputation {.tabset}

### Imputation calculation
```{r seurat_imputation}


if(long.compute){
  
  seurat.list <- lapply(seurat.list, 
                        FUN = function(x){
                          SeuratWrappers::RunALRA(x, genes.use = rownames(x))
                        }
  )
  
  # Save dataset with dim reduction
  saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list_imputed.rds")
  
}


```



## Differential gene expression {.tabset}

### DEG calculation
```{r DEG_calculation}

if(long.compute){
  for(i in seq_along(seurat.list)){
    DefaultAssay(seurat.list[[i]]) <- "SCT"
  }

  #BiocManager::install('limma')
  library("limma")
  
  
  markers.vec <- lapply(seurat.list, 
                        FUN = Seurat::FindAllMarkers,
                        only.pos = FALSE)
  
  
  
  # Save dataset with dim reduction
  saveRDS(markers.vec, "Exported_RDS_files/DEG_markers.rds")
  
  
  
  # just cluster 4 specific markers
  cluster.4.markers <- FindMarkers(seurat.list$Healthy, 
                                   ident.1 = 4)
  
  # Save dataset with dim reduction
  saveRDS(cluster.4.markers, "Exported_RDS_files/DEG_markers_cluster_4.rds")
  
}

```
 
 

### DEG visualisation 
```{r DEG_vis}


  for(i in seq_along(seurat.list)){
    DefaultAssay(seurat.list[[i]]) <- "alra"
    
    Idents(seurat.list[[i]]) <- "seurat_clusters"
  }




top.genes <- markers.vec$Healthy %>%
  dplyr::filter(p_val_adj < 0.05) %>%
  group_by(cluster) %>%
  top_n(30, avg_log2FC) %>%
  pull(gene)

top.genes <- markers.vec$Healthy %>%
  dplyr::filter(p_val_adj < 0.05) %>%
  dplyr::filter(cluster == 4) %>%
  top_n(50, avg_log2FC) %>%
  pull(gene)


small.object <- subset(seurat.list$Healthy, downsample = 300)

small.object <- ScaleData(small.object)



DoHeatmap(small.object,
          assay = "alra",
          features = top.genes, 
          draw.lines = FALSE)


up.genes <- cluster.4.markers %>%
  dplyr::filter(p_val_adj < 0.05)  %>%
  top_n(20, avg_log2FC)

dn.genes <- cluster.4.markers %>%
  dplyr::filter(p_val_adj < 0.05)  %>%
  top_n(-20, avg_log2FC)



top.genes <- c(rownames(up.genes), rownames(dn.genes), "NCAM1")





DoHeatmap(small.object,
          assay = "alra",
          features = top.genes, 
          draw.lines = FALSE)


##


#








DoHeatmap(small.object,
          assay = "alra",
          features = top.genes, 
          draw.lines = FALSE)






Nebulosa::plot_density(seurat.list$Healthy, 
                       "EOMES")









FeaturePlot(seurat.list$Healthy, 
            c("NCAM1", "FCGR3A"), 
            pt.size = 0.5,
            cols = c("gray", "red", "blue"),
            order = TRUE,
            blend = TRUE)



UMAPPlot(seurat.list$Healthy, label = T)




FeaturePlot(seurat.list$Healthy, 
            "BATF3", 
            pt.size = 0.4,
            order = TRUE)









for(i in seq_along())

FeaturePlot(seurat.list$Healthy, 
            "IL7R", 
            pt.size = 0.5,
            order = TRUE)



FeaturePlot








Idents(seurat.list$Healthy) <- "seurat_clusters"

small.object <- subset(seurat.list$Healthy, downsample = 300)



small.object <- ScaleData(small.object)


goi <- c("LTB", "IL7R", "KIT", "BATF3", "DLL1", "ID3", "INPP4B", "DPP4", "IL2RA", "ITGA1", "EOMES", "SELL", "KLRG1", "TNFSF10", "NKG7", "TNF", "GZMA", "GZMB", "PRF1", "CD7", "CD9")


DoHeatmap(small.object,
          assay = "alra",
          features = goi, 
          draw.lines = FALSE)









DefaultAssay(human.seurat.filt) <- "alra"


output.dir <- "output/figures/Key_marker_genes"


  if(!dir.exists(paste0(output.dir))){
    dir.create(paste0(output.dir), 
               recursive = TRUE)}



for(i in seq_along(goi)){
  if(goi[i] %in% rownames(human.seurat.filt@assays$alra@data)){
    
    print(FeaturePlot(human.seurat.filt, 
                      feature = goi[i]))
    
    dev.copy(pdf, paste0(output.dir, "/FeaturePlot_", goi[i], "_imputed.pdf"))
    dev.off()
    
    print(VlnPlot(human.seurat.filt, 
                  feature = goi[i],
                  assay = "alra",
                  pt.size = 0.1))
    
    dev.copy(pdf, paste0(output.dir, "/VlnPlot_", goi[i], "_imputed.pdf"))
    dev.off()
  }
}










VlnPlot(human.seurat.filt, 
                  feature = "Up_sig1",
                  pt.size = 0.1)





average.object <- AverageExpression(human.seurat.filt, return.seurat = TRUE)


DefaultAssay(average.object) <- "alra"

average.object <- ScaleData(average.object)


DoHeatmap(average.object,
          assay = "alra",
          features = goi, 
          draw.lines = FALSE)














goi <- c("CD7", "SELL", "CD160", "ITGAM", "CXCR6", "ITGA1", "ITGA2", "CD226", "EOMES", "IL7R", LTB)
goi <- Up.genes



FeaturePlot(human.seurat.filt, 
            feature = "LTB")


human.seurat.filt@meta.data$Up_sig1


rownames(human.seurat.filt@assays$RNA@data)[grepl("CD2", rownames(human.seurat.filt@assays$RNA@data))]


goi <- c("LTB", "KIT", "CD160", "IL7R", "NKG7", "GZMA", "IFNG", "IFNGR1", "IFNGR2", "EOMES")

sort(rowSums(human.seurat.filt@assays$RNA@data), decreasing = T)[20:30]


rownames(human.seurat.filt@assays$RNA@data)


FeaturePlot(human.seurat.filt,
              "ZNF683", 
              pt.size = 0.5,
              order = TRUE)



Up.genes

VlnPlot(human.seurat.filt,
              "Dn_sig1", pt.size = 0.1)






# Read in CD160 signature
CD160.sig <- read.csv("Data/QLF_S.PosvsNeg.csv")

Up.genes <- 
  CD160.sig %>%
  dplyr::filter(FDR < 0.05) %>%
  dplyr::top_n(100, logFC) %>%
  dplyr::arrange(desc(logFC)) %>%
  dplyr::pull(genes)

Up.genes <- toupper(Up.genes)



Dn.genes <- 
  CD160.sig %>%
  dplyr::filter(FDR < 0.05) %>%
  dplyr::top_n(-100, logFC) %>%
  dplyr::arrange(logFC) %>%
  dplyr::pull(genes)

Dn.genes <- toupper(Dn.genes)




##########################
# Do signature scoring
##########################

# Set default assay to RNA
DefaultAssay(human.seurat.filt) <- "RNA"


human.seurat.filt <- AddModuleScore(human.seurat.filt, 
                                    features = list(Up.genes), 
                                    name = "Up_sig",
                                    ctrl = 80,
                                    seed = 42)

human.seurat.filt <- AddModuleScore(human.seurat.filt, 
                                    features = list(Dn.genes), 
                                    name = "Dn_sig",
                                    ctrl = 80,
                                    seed = 42)


#########################################
# Visualise signature and sig genes
#########################################

DefaultAssay(mouse.seurat.filt) <- "alra"



for(i in seq_along(Up.genes)){
  
  
  if(Up.genes[i] %in% rownames(mouse.seurat.filt@assays$alra@data)){
  print(VlnPlot(mouse.seurat.filt,
        assay = "alra",
        features = paste0(Up.genes[i]),
        pt.size = 0.1,
        group.by = "seurat_clusters"))

  
  dev.copy(pdf, paste0(output.dir, "/VlnPlots/VlnPlot_", Up.genes[i], "_imputed.pdf"))
  dev.off()
  
  
  
  print(Nebulosa::plot_density(mouse.seurat.filt,
                         paste0(Up.genes[i])))
  
dev.copy(pdf, paste0(output.dir, "/Density_UMAP/Nebulosa_", Up.genes[i], "_imputed.pdf"))
  dev.off()
  
  
  print(FeaturePlot(mouse.seurat.filt,
              paste0(Up.genes[i]), 
              pt.size = 0.5,
              order = TRUE))
  
dev.copy(pdf, paste0(output.dir, "/UMAP/FeaturePlot_", Up.genes[i], "_imputed.pdf"))
  dev.off()
  
  
  }
  
}




VlnPlot(mouse.seurat.filt, 
        "Up_sig1", 
        group.by = "seurat_clusters",
        pt.size = 0.1)

dev.copy(pdf, paste0(output.dir, "/Cd160_signature_upregulated_genes_imputed.pdf"))
dev.off()


VlnPlot(mouse.seurat.filt,
        "Dn_sig1",
        group.by = "seurat_clusters", 
        pt.size = 0.1)

dev.copy(pdf, paste0(output.dir, "/Cd160_signature_downregulated_genes_imputed.pdf"))
dev.off()






ILC1.signature <- c("Cd160", "Xcl1", "Crtam", "Batf3", "Id3", "Ltb", "Tnfsf10")
NK.signature <- c("Itgam", "Eomes", "Gzmb")









# Scatter plot across individual features, repleaces CellPlot

DimHeatmap(object = seurat.list$Healthy, reduction = "pca", cells = 100)


plot <- DimPlot(object = seurat.list$Healthy) + NoLegend()

# HoverLocator replaces the former `do.hover` argument It can also show extra data throught the `information` argument,
# designed to work smoothly with FetchData
HoverLocator(plot = plot, information = FetchData(object = seurat.list$Healthy, vars = c("ident", "PC_1", "nFeature_RNA")))

# FeatureLocator replaces the former `do.identify`
select.cells <- CellSelector(plot = plot)


```
