---
title: "Crinier_2020_Human_BM_NK_preprocessing"
author: "Dillon Corvino"
date: "11/08/2021"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: united
    highlight: tango
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

Built with R version `r getRversion()`

## Setup {.tabset}

### Dataset information
```{r Dataset_Info}




```

### Environment
```{r setup}

knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,  
  eval = TRUE, 
  tidy = TRUE
)

knitr::opts_knit$set(
  root.dir = "../"
)


# Environment Set up
rm(list = ls()) #Clean workspace
cat("\014")     #Clean Console
gc() # Free memory

# Establish working directory
library("rstudioapi")

# Set working directory to source file location
setwd(dirname(getActiveDocumentContext()$path))
setwd("..")

# Load packages
source("R/Load_packages.R", local = knitr::knit_global())

# Create output directories & load custom functions & colour scheme
source("R/Setup.R", local = knitr::knit_global())

long.compute <- FALSE
quick.load <- TRUE


if(quick.load){
  
  cluster.4.markers <- readRDS("Exported_RDS_files/DEG_markers_cluster_4.rds")
  markers.vec <- readRDS("Exported_RDS_files/DEG_markers.rds")
  seurat.list <- readRDS("Exported_RDS_files/Human_dataset_seurat_list_imputed.rds")
  
  
}
```

### Read and format dataset
```{r reading_data}

if(long.compute){
  # List files 
  data.list <- list.files("Data/GSE159624_RAW/", pattern = ".csv")
  
  
  ############################
  # Read in sample data
  ############################
  
  # Create name variable
  file.names <- gsub("_normalized.csv", "", data.list)
  file.names <- gsub("GSM([0-9]+)_", "", file.names)
  file.names
  
  
  
  
  # Read in samples
  for (i in seq_along(data.list)){
    assign(file.names[i], read.csv(paste0("Data/GSE159624_RAW/", data.list[i])))
  }
  
  
  
  
  # Annotate the cell ids so can be identified later
  for(i in 1:8){
    
    AML <- eval(parse(text = paste0("AML_donor", i)))
    Healthy <- eval(parse(text = paste0("Healthy_donor", i)))
    
    
    
    colnames(AML) <- paste0(colnames(AML), "_AML_", i)
    colnames(Healthy) <- paste0(colnames(Healthy), "_Healthy_", i)
    
    colnames(AML)[1] <- "GeneID"
    colnames(Healthy)[1] <- "GeneID"
    
    assign(paste0("AML_donor", i), AML)
    assign(paste0("Healthy_donor", i), Healthy)
    
  }
  
  
  Healthy_donor1$GeneID
  
  ########################################
  # Merge data by organ of origin
  ########################################
  
  # Dplyr doesnt allow merge by rowname. so have to make it a variable and then return the variable
  
  healthy.dataset <- 
    full_join(Healthy_donor1, Healthy_donor2,  by = "GeneID") %>%
    full_join(Healthy_donor3,  by = "GeneID") %>%
    full_join(Healthy_donor4,  by = "GeneID") %>%
    full_join(Healthy_donor5,  by = "GeneID") %>%
    full_join(Healthy_donor6,  by = "GeneID") %>%
    full_join(Healthy_donor7,  by = "GeneID") %>%
    full_join(Healthy_donor8,  by = "GeneID") %>%
    arrange(desc = TRUE) %>%
    column_to_rownames(var = "GeneID")
  
  
  
  
  AML.dataset <- 
    full_join(AML_donor1, AML_donor2,  by = "GeneID") %>%
    full_join(AML_donor3,  by = "GeneID") %>%
    full_join(AML_donor4,  by = "GeneID") %>%
    full_join(AML_donor5,  by = "GeneID") %>%
    full_join(AML_donor6,  by = "GeneID") %>%
    full_join(AML_donor7,  by = "GeneID") %>%
    full_join(AML_donor8,  by = "GeneID") %>%
    arrange(desc = TRUE) %>%
    column_to_rownames(var = "GeneID")
  
  
  
  
  
  
  
  # Checking all genes were merged 
  AML.geneIDs <- unique(c(as.character(AML_donor1$GeneID), 
                          as.character(AML_donor2$GeneID), 
                          as.character(AML_donor3$GeneID), 
                          as.character(AML_donor4$GeneID), 
                          as.character(AML_donor5$GeneID), 
                          as.character(AML_donor6$GeneID), 
                          as.character(AML_donor7$GeneID), 
                          as.character(AML_donor8$GeneID)))
  
  length(AML.geneIDs) == nrow(AML.dataset)
  
  # overview stats
  dim(healthy.dataset)
  dim(AML.dataset)
  
  #####################
  # Format dataframe
  #####################
  
  
  
  # Merge all data together
  Human.dataset <- merge(healthy.dataset, AML.dataset, 
                         by = "row.names", 
                         all = TRUE)
  
  # Annotate
  rownames(Human.dataset) <- Human.dataset$Row.names
  
  index.val <- grep("^Row.names$", colnames(Human.dataset))
  colnames(Human.dataset)[index.val]
  Human.dataset <- Human.dataset[,-index.val]
  
  
  
  
  # When a gene was detected in AML or Healthy but not the other there are now NA values for this entry in the other dataset cells
  # Remove NA values
  na.values <- is.na(Human.dataset)
  sum(na.values) # 14,8438,953
  
  # Assigning NA values as 0
  Human.dataset[na.values] <- 0
  
  # Checking NA values are removed
  sum(is.na(Human.dataset)) 
  
  dim(Human.dataset) # 18,232 genes and 39,628 cells 
  
  # Write data to file for easy use later
  write.csv(Human.dataset, "output/tables/Human_AML_and_Healthy.csv")
  saveRDS(Human.dataset, "Exported_RDS_files/Human_AML_and_Healthy.rds")
  saveRDS(AML.dataset, "Exported_RDS_files/Human_AML.rds")
  saveRDS(healthy.dataset, "Exported_RDS_files/Human_Healthy.rds")
  
  # remove large datafiles
  rm(Healthy_donor1, Healthy_donor2, Healthy_donor3, 
     Healthy_donor4, Healthy_donor5, Healthy_donor6, 
     Healthy_donor7, Healthy_donor8, 
     AML_donor1, AML_donor2, AML_donor3, AML_donor4, 
     AML_donor5, AML_donor6, AML_donor7, AML_donor8, AML, Healthy)
  
}


```

### Create seurat object
```{r create_Seurat_object}

if(long.compute){
# load data, create seurat object and calcualte mito percentage
load_data <- function(data.dir){
  data <- readRDS(data.dir)
  
  project.name <- gsub("Exported_RDS_files/", "", data.dir)
  project.name <- gsub(".rds", "", project.name)
  
  s.object <- CreateSeuratObject(counts = data,
                                 min.cells = 3, 
                                 project = project.name,
                                 min.genes = 200)
  
  s.object <- PercentageFeatureSet(s.object,
                                   pattern = "^MT-",
                                   col.name = "percent.mt")
  
  return(s.object)
}


healthy.dataset <- load_data("Exported_RDS_files/Human_Healthy.rds")

AML.dataset <- load_data("Exported_RDS_files/Human_AML.rds")


# Make a list of seurat objects
seurat.list <- c(healthy.dataset, AML.dataset)
names(seurat.list) <- c("Healthy", "AML")

saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list.rds")

# remove single seurat objects
rm(healthy.dataset, AML.dataset)

}
```



## QC and Filter {.tabset}

### QC & filter

```{r QC_and_filter}

if(long.compute){
  
  for(i in seq_along(seurat.list)){
    
    # Create output dir
    output.path <- paste0("output/QC/QC_", names(seurat.list)[i])
    
    
    if(!dir.exists(output.path)){
      dir.create(output.path, 
                 recursive = TRUE)}
    
    
    # Plot QC metrics 
    
    # nFeature & nCount & Mito
    print(
      VlnPlot(seurat.list[[i]], 
              features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), 
              pt.size = 0.1)
    )
    
    dev.copy(pdf,  paste0(output.path, "/QC_nFeature_nCount_RNA_percentMito.pdf"))
    dev.off()
    
    # Mito
    print(
      VlnPlot(seurat.list[[i]], 
              features = "percent.mt", 
              y.max = 20,
              pt.size = 0.1)
    )
    
    dev.copy(pdf,  paste0(output.path, "/QC_RNA_percentMito.pdf"))
    dev.off()
    
  }
  
  
  min.nFeature <- 400
  max.nFeature <- 3000
  max.nCount <- 3000
  max.Percent.Mt <- 5
  
  seurat.list <- lapply(seurat.list, 
                        FUN = subset,
                        subset = nFeature_RNA > min.nFeature & nFeature_RNA < max.nFeature & nCount_RNA < max.nCount & percent.mt < max.Percent.Mt)
  
  
  
  
  for(i in seq_along(seurat.list)){
    
    # output.dir
    output.path <- paste0("output/QC/QC_", names(seurat.list)[i])
    
    # After filtering
    print(
      VlnPlot(seurat.list[[i]],
              features = c("nFeature_RNA", "nCount_RNA", "percent.mt"),
              pt.size = 0.1)
    )
    
    dev.copy(pdf,  paste0(output.path, "/QC_nFeature_nCount_RNA_percentMito_Postfiltering.pdf"))
    dev.off()
    
  }
  

  # Post-filtering metrics
  seurat.list
  
  
  # Save filtered dataset
  saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list.rds")
  
  
}

```


## SCT normalise data

```{r SCT_normalisation}

if(long.compute){
# Normalise and scale with SCTransform 
seurat.list <- lapply(X = seurat.list, 
                      FUN = SCTransform, 
                      method = "glmGamPoi", 
                      vars.to.regress = "percent.mt", 
                      verbose = TRUE) 
  

 # Save normalised dataset
  saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list.rds")
  
}

```



## Combine patients {.tabset}

### Integrate data

```{r Integrate_patients}

if(long.compute){
  
  
  # Integrate datasets
  
  # Select features
  integration.features <- SelectIntegrationFeatures(object.list = seurat.list, 
                                                    nfeatures = 4000)
  
  # Prep dataset
  integrated.seurat <- PrepSCTIntegration(object.list = seurat.list, 
                                          anchor.features = integration.features)
  
  # perform PCA analysis
  integrated.seurat <- lapply(X = seurat.list, 
                              FUN = Seurat::RunPCA,
                              features = integration.features)
  
  
  # Find integration anchors
  integration.anchors <- FindIntegrationAnchors(object.list = integrated.seurat, 
                                                anchor.features = integration.features,
                                                normalization.method = 'SCT',
                                                reduction = "rpca", # rpca is more conservative, best for datasets which may not overlap alot
                                                k.anchor = 20) # increases strength of alignment
  
  # Integrate dataset
  integrated.seurat <- IntegrateData(anchorset = integration.anchors, 
                                     normalization.method = 'SCT')
  
  
  # Basic overview of data
  integrated.seurat # 30,04 genes and 5,060 cells 
  
  seurat.list[[1]] # 24,231 cells
  seurat.list[[2]] # 15,293 cells
  
  # Save files 
  saveRDS(integrated.seurat, file = "Exported_RDS_files/integrated_seurat.rds")
  
  # Remove unneeded data
  rm(integration.anchors, integration.features, features)
  
}


```




## Unbiased Clustering {.tabset}

### Clustering
```{r PCA_and_cluster_identification}

if(long.compute){

################################
# PCA and cluster identification
################################


# Set seed for reproducibility
set.seed(42)


# Calculate PCA
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::RunPCA,
                      npcs = 20, 
                      verbose = TRUE, 
                      rev.pca = TRUE,
                      seed.use = 42)

# Find neighbours
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::FindNeighbors,
                      dims = 1:20)

# Find clusters
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::FindClusters,
                      resolution = 0.1)



# Plot PCA
for(i in seq_along(seurat.list)){
  
  # Create output dir
  output.path <- paste0("output/figures/PCA_", names(seurat.list)[i])
  
  if(!dir.exists(output.path)){
    dir.create(output.path, 
               recursive = TRUE)}
  
  
  print(
    PCAPlot(seurat.list[[i]], 
            dims = c(1, 2),
            pt.size = 2, 
            group.by = "orig.ident")
  )
  
  dev.copy(pdf,  paste0(output.path, "/PCA_dim1_vs_2.pdf"))
  dev.off()
  
  
  print(
    PCAPlot(seurat.list[[i]], 
            dims = c(2, 3),
            pt.size = 2, 
            group.by = "orig.ident")
  )
  
  dev.copy(pdf,  paste0(output.path, "/PCA_dim2_vs_3.pdf"))
  dev.off()
  
  
  
}



#################################################################
# Determine statistically significant principal components
#################################################################

for(i in seq_along(seurat.list)){
  
  # get output.dir
  output.path <- paste0("output/figures/PCA_", names(seurat.list)[i])
  
  print(
    ElbowPlot(seurat.list[[i]],
              ndims = 20)
  )
  
  dev.copy(pdf,  paste0(output.path, "/PC_elbowplot.pdf"))
  dev.off()
}


}






# Not applicable for SCT-transformed 

if(long.compute){
  
  # NOTE: This process can take a long time for big datasets, comment out for
# expediency.  More approximate techniques such as those implemented in
# PCElbowPlot() can be used to reduce computation time
  
  
    seurat.list <- lapply(seurat.list, 
           FUN = Seurat::JackStraw,
           reduction = "pca", 
           dims = 50)
    
    seurat.list <- lapply(seurat.list, 
           FUN = Seurat::ScoreJackStraw,
           dims = 1:50)
    
    
      for(i in seq_along(seurat.list)){

      # get output.dir
  output.path <- paste0("output/figures/PCA_", names(seurat.list)[i])
  
  print(
    JackStrawPlot(seurat.list[[i]],
                  dims = 1:30)
  )
  
   dev.copy(pdf,  paste0(output.path, "/JackStrawPlot.pdf"))
  dev.off()
  
  }
}


```


### UMAP and tSNE dim Reduction
```{r Dim_reduction}

if(long.compute){

# Calculate tSNE
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::RunTSNE,
                      reduction = "pca",
                      dims = 1:20,
                      perplexity = 30,
                      method = "FIt-SNE",
                      seed.use = 42,
                      dim.embed = 2)

# Plot tSNE
for(i in seq_along(seurat.list)){
  
  # Create output dir
  output.path <- paste0("output/figures/tSNE_", names(seurat.list)[i])
  
  if(!dir.exists(output.path)){
    dir.create(output.path, 
               recursive = TRUE)}
  
  
  print(
    TSNEPlot(seurat.list[[i]], 
             group.by = "orig.ident")
  )
  
  dev.copy(pdf,  paste0(output.path, "/tSNE_orig_ident.pdf"))
  dev.off()
  
  
  print(
    TSNEPlot(seurat.list[[i]], 
             group.by = "seurat_clusters")
  )
  
  dev.copy(pdf,  paste0(output.path, "/tSNE_seurat_clusters.pdf"))
  dev.off()
  
  
}


 # Calculate UMAP
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::RunUMAP,
                      reduction = "pca",
                      dims = 1:20,
                      umap.method = "uwot", 
                      n.neighbors = 45, # 5 to 50 // 45
                      min.dist = 0.5, # Sensible values are in the range 0.001 to 0.5 // 0.5
                      seed.use = 42)

# Plot UMAP
for(i in seq_along(seurat.list)){
  
  # Create output dir
  output.path <- paste0("output/figures/UMAP_", names(seurat.list)[i])
  
  if(!dir.exists(output.path)){
    dir.create(output.path, 
               recursive = TRUE)}
  
  
  print(
    UMAPPlot(seurat.list[[i]], 
             group.by = "orig.ident")
  )
  
  dev.copy(pdf,  paste0(output.path, "/UMAP_orig_ident.pdf"))
  dev.off()
  
  
  print(
    UMAPPlot(seurat.list[[i]], 
             group.by = "seurat_clusters")
  )
  
  dev.copy(pdf,  paste0(output.path, "/UMAP_seurat_clusters.pdf"))
  dev.off()
  
  
}

# Save dataset with dim reduction
saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list.rds")


}
```



## Imputation {.tabset}

### Imputation calculation
```{r seurat_imputation}


if(long.compute){
  
  seurat.list <- lapply(seurat.list, 
                        FUN = function(x){
                          SeuratWrappers::RunALRA(x, genes.use = rownames(x))
                        }
  )
  
  # Save dataset with dim reduction
  saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list_imputed.rds")
  
}


```


### Rename clusters
```{r Rename_clusters}

Idents(seurat.list$Healthy) <- "seurat_clusters"

seurat.list$Healthy <- RenameIdents(seurat.list$Healthy,
                                    "0" = "NK", 
                                    "1" = "NK", 
                                    "2" = "NK", 
                                    "3" = "NK", 
                                    "4" = "ILC1-like", 
                                    "5" = "NK", 
                                    "6" = "NK")


seurat.list$Healthy@meta.data$named_clusters <- Idents(seurat.list$Healthy)

# save seurat list with metadata
saveRDS(seurat.list, "Exported_RDS_files/Human_dataset_seurat_list_imputed.rds")

```



## Differential gene expression {.tabset}

### DEG calculation
```{r DEG_calculation}

if(long.compute){
  for(i in seq_along(seurat.list)){
    DefaultAssay(seurat.list[[i]]) <- "SCT"
    Idents(seurat.list[[i]]) <- "seurat_clusters"
  }
  
  #BiocManager::install('limma')
  library("limma")
  
  
  markers.vec <- lapply(seurat.list, 
                        FUN = Seurat::FindAllMarkers,
                        only.pos = FALSE)
  
  
  
  # Save dataset with dim reduction
  saveRDS(markers.vec, "Exported_RDS_files/DEG_markers.rds")
  
  
  
  # just cluster 4 specific markers
  cluster.4.markers <- FindMarkers(seurat.list$Healthy, 
                                   ident.1 = 4)
  
  # Save dataset with dim reduction
  saveRDS(cluster.4.markers, "Exported_RDS_files/DEG_markers_cluster_4.rds")
  
  
  # Cluster 4 vs 6
  cluster.4.vs.6.markers <- FindMarkers(seurat.list$Healthy, 
                                   ident.1 = 4, 
                                   ident.2 = 6)
  
  # 
  saveRDS(cluster.4.vs.6.markers, "Exported_RDS_files/DEG_markers_cluster_4_vs_6.rds")
  
  
  # Named clusters DEGs
  Idents(seurat.list$Healthy) <- "named_clusters"
  
  markers.named.clusters <- Seurat::FindAllMarkers(seurat.list$Healthy,
                                            only.pos = FALSE)
  
  # Save dataset with dim reduction
  saveRDS(markers.named.clusters, "Exported_RDS_files/DEG_markers_named_clusters.rds")
  
}

```
 
 

### Module score calculation
```{r Module_score_calculation}

# Create output directories
if(!dir.exists("output/figures/CD160_sig_module_score")){
  dir.create("output/figures/CD160_sig_module_score", 
             recursive = T)
}



for(i in seq_along(seurat.list)){
  DefaultAssay(seurat.list[[i]]) <- "SCT"
  
  Idents(seurat.list[[i]]) <- "named_clusters"
}


# Read in CD160 signature
CD160.sig <- read.csv("Data/QLF_S.PosvsNeg.csv")

Up.genes <- 
  CD160.sig %>%
  dplyr::filter(FDR < 0.05) %>%
  dplyr::top_n(100, logFC) %>%
  dplyr::arrange(desc(logFC)) %>%
  dplyr::pull(genes)

Up.genes <- convertMouseGeneList(Up.genes)

Dn.genes <- 
  CD160.sig %>%
  dplyr::filter(FDR < 0.05) %>%
  dplyr::top_n(-100, logFC) %>%
  dplyr::arrange(logFC) %>%
  dplyr::pull(genes)

Dn.genes <- convertMouseGeneList(Dn.genes)


# Add module score
seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::AddModuleScore,
                      features = list(Up.genes), 
                      name = "Up_sig",
                      ctrl = 80,
                      seed = 42)


seurat.list <- lapply(seurat.list, 
                      FUN = Seurat::AddModuleScore,
                      features = list(Dn.genes), 
                      name = "Dn_sig",
                      ctrl = 80,
                      seed = 42)



# visualise module score 
VlnPlot(seurat.list$Healthy, 
        "Up_sig1",
        pt.size = 0)

dev.copy(pdf, "output/figures/CD160_sig_module_score/VlnPlot_Upregulated_signature.pdf")
dev.off()

VlnPlot(seurat.list$Healthy,
        "Dn_sig1",
        pt.size = 0)

dev.copy(pdf, "output/figures/CD160_sig_module_score/VlnPlot_Downregulated_signature.pdf")
dev.off()


# Heatmaps
DefaultAssay(seurat.list$Healthy) <- "alra"

Idents(seurat.list$Healthy) <- "named_clusters"

small.object <- subset(seurat.list$Healthy, downsample = 300)

small.object <- ScaleData(small.object)

DoHeatmap(small.object,
          assay = "alra",
          features = Up.genes, 
          draw.lines = FALSE)

dev.copy(pdf, "output/figures/CD160_sig_module_score/Heatmap_Upregulated_signature.pdf")
dev.off()

DoHeatmap(small.object,
          assay = "alra",
          features = Dn.genes, 
          draw.lines = FALSE)

dev.copy(pdf, "output/figures/CD160_sig_module_score/Heatmap_Downregulated_signature.pdf")
dev.off()


```
 
 
### DEG Heatmaps
```{r Heatmaps}

for(i in seq_along(seurat.list)){
  DefaultAssay(seurat.list[[i]]) <- "alra"
  
  Idents(seurat.list[[i]]) <- "named_clusters"
}



# Create output directories
if(!dir.exists("output/figures/Heatmaps_healthy")){
  dir.create("output/figures/Heatmaps_healthy", 
             recursive = T)
}



# Prepare dataset for heatmap visualisation
DefaultAssay(seurat.list$Healthy) <- "alra"

Idents(seurat.list$Healthy) <- "named_clusters"

small.object <- subset(seurat.list$Healthy, downsample = 300)

small.object <- ScaleData(small.object)


markers.named.clusters <- readRDS("Exported_RDS_files/DEG_markers_named_clusters.rds")


NK.genes <- 
  markers.named.clusters %>%
  dplyr::filter(p_val_adj < 0.05) %>%
  dplyr::filter(cluster == "NK") %>%
  dplyr::top_n(20, avg_log2FC) %>%
  dplyr::arrange(desc(avg_log2FC)) %>%
  dplyr::pull(gene)

ILC.genes <- 
  markers.named.clusters %>%
  dplyr::filter(p_val_adj < 0.05) %>%
  dplyr::filter(cluster == "ILC1-like") %>%
  dplyr::top_n(20, avg_log2FC) %>%
  dplyr::arrange(desc(avg_log2FC)) %>%
  dplyr::pull(gene)

goi <- c(ILC.genes, NK.genes)


DoHeatmap(small.object,
          assay = "alra",
          features = goi, 
          raster = FALSE,
          draw.lines = FALSE)

dev.copy(pdf, "output/figures/Heatmaps_healthy/Top_20_DEGs.pdf")
dev.off()


# Custom heatmap

goi <- c("IL7R", "LTB", "XCL1", "ID3", "KIT", "CSF2", "CCR7", "INPP4B", "GPR183", "DLL1", "IL23R", "KLRD1", "NCR1", 
         "EOMES", "TBX21", "GZMA", "GZMB", "NKG7", "PRF1", "GNLY", "CD160", "KLRG1", "CX3CR1", "ZEB2")


DoHeatmap(small.object,
          assay = "alra",
          features = goi, 
          raster = FALSE,
          draw.lines = FALSE)

dev.copy(pdf, "output/figures/Heatmaps_healthy/Custom_heatmap.pdf")
dev.off()


# KIR and KLR genes

goi <- c("KIR3DL3", "KIR2DL3", "KIR2DL1", "KIR2DL4", "KIR3DL1", "KIR3DL2",
         "KLRG1",  "KLRB1",  "KLRF1",  "KLRD1",  "KLRK1",  "KLRC4",  "KLRC3",  "KLRC2",  "KLRC1", "CD2")


DoHeatmap(small.object,
          assay = "alra",
          features = goi, 
          raster = FALSE,
          draw.lines = FALSE)

dev.copy(pdf, "output/figures/Heatmaps_healthy/KIR_KLR_heatmap.pdf")
dev.off()


# Transcription_factors
goi <- c("GATA3", "TCF7", "AHR", "SOX4", "RUNX2", "ZEB1", "MYC", "AFF3", "SSBP2", "TCF4", "HOXA5",
         "IKZF3",  "TBX21",  "NFIL3",  "ZEB2",  "PRDM1",  "RORA", "LEF1")


DoHeatmap(small.object,
          assay = "alra",
          features = goi, 
          raster = FALSE,
          draw.lines = FALSE)

dev.copy(pdf, "output/figures/Heatmaps_healthy/TF_heatmap.pdf")
dev.off()

```
 
 
### VlnPlots
```{r Vlnplots}

for(i in seq_along(seurat.list)){
  DefaultAssay(seurat.list[[i]]) <- "alra"
  
  Idents(seurat.list[[i]]) <- "named_clusters"
}


# Create output directories
if(!dir.exists("output/figures/VlnPlots")){
  dir.create("output/figures/VlnPlots", 
             recursive = T)
}



goi <- c("NCAM1", "FCGR3A", "IL7R", "LTB", "KLRB1")

for(i in seq_along(goi)){
  print(
    VlnPlot(seurat.list$Healthy,
            feature = goi[i], 
            group.by = "named_clusters",
            pt.size = 0)
  )
  dev.copy(pdf, paste0("output/figures/VlnPlots/Imputed_", goi[i], "_healthy_dataset.pdf"))
  dev.off()
}

```
 
### UMAP cluster plot
```{r UMAP_clusters}

 # Create output directories
if(!dir.exists("output/figures/UMAP_Healthy")){
  dir.create("output/figures/UMAP_Healthy", 
             recursive = T)
}


UMAPPlot(seurat.list$Healthy, 
         group.by = "named_clusters", 
         cols = c("Gray", "Orange"))

dev.copy(pdf, "output/figures/UMAP_Healthy/UMAP_named_clusters.pdf")
dev.off()



barplot(prop.table(table(seurat.list$Healthy@meta.data$named_clusters))*100)

```
 
 
## GSEA analysis {.tabset}

### Scillus

```{r Scillus_GSEA}

# Create output directories
if(!dir.exists("output/figures/GO_analysis")){
  dir.create("output/figures/GO_analysis", 
             recursive = T)
}

for(i in seq_along(seurat.list)){
  DefaultAssay(seurat.list[[i]]) <- "alra"
  
  Idents(seurat.list[[i]]) <- "seurat_clusters"
}

# Using the Scillus package


# Filter DEGs by sig and foldchange
GO.markers <- markers.vec$Healthy %>%
  dplyr::filter(p_val_adj < 0.05 & avg_log2FC > 0.25)




# number of genes DEG per cluster 
table(GO.markers$cluster) # Used o justify using topn value = 100

####################
# Analysis variables 
####################
organism <- "human"
n.val <- 100

# Plot Gene Ontology analysis

# CC 
pdf("output/figures/GO_analysis/GO_CC.pdf", width = 20, height = 20)

plot_all_cluster_go(GO.markers,
                    topn = n.val,
                    org = organism, 
                    ont = "CC")

dev.off()


# BP 
pdf("output/figures/GO_analysis/GO_BP.pdf", width = 20, height = 20)

plot_all_cluster_go(GO.markers,
                    topn = n.val,
                    org = organism, 
                    ont = "BP")

dev.off()

# MF 
pdf("output/figures/GO_analysis/GO_MF.pdf", width = 20, height = 20)

plot_all_cluster_go(GO.markers,
                    topn = n.val,
                    org = organism, 
                    ont = "MF")
dev.off()


```


### GSEA
```{r GSEA}


test_GSEA.v2 <- function (diff, clusters = NULL, pathway) 
{ #browser()
    if (!requireNamespace("fgsea", quietly = TRUE)) {
        stop(paste("Package \"fgsea\" needed for this function to work. Please install it."), 
            call. = FALSE)
    }
    if (is.null(clusters)) 
        clusters <- unique(diff$cluster)
    gsea_res <- list()
    for (i in seq(length(clusters))) {
        data <- diff %>% filter(.data$cluster == clusters[i]) %>% 
            arrange(desc(.data$avg_log2FC))
        l <- data$avg_log2FC
        names(l) <- data$feature
        res <- fgsea::fgsea(pathways = pathway, stats = l, minSize = 15, 
            maxSize = 500)
        res <- res %>% add_column(cluster = clusters[i], .before = 1)
        gsea_res[[i]] <- res
    }
    return(as_tibble(do.call("rbind", gsea_res)))
}


if(long.compute){
  for(i in seq_along(seurat.list)){
    DefaultAssay(seurat.list[[i]]) <- "SCT"
  }

  #BiocManager::install('limma')
  library("limma")
  
  Idents(seurat.list$Healthy) <- "named_clusters"
  
  markers.vec.all <- Seurat::FindAllMarkers(seurat.list$Healthy, 
                                            logfc.threshold = 0,
                                            min.cells.group = 1,
                                            only.pos = TRUE)
  
  # Save dataset with dim reduction
  saveRDS(markers.vec.all, "Exported_RDS_files/DEG_markers_no_thresholds.rds")
}


markers.vec.all$features <- markers.vec.all$gene



gsea_res <- test_GSEA.v2(markers.vec.all,
                         pathway = pathways.hallmark)


plot_GSEA(gsea_res,
          p_cutoff = 0.1, 
          colors = c("#0570b0", "grey", "#d7301f"))


```
 
 
 
 
 
 
 
 
 
 ### Cell cycle analysis
```{r cell_cycle}

if(!dir.exists("output/figures/cell_cycle")){
  dir.create("output/figures/cell_cycle")
}



for(i in seq_along(seurat.list)){
  DefaultAssay(seurat.list[[i]]) <- "SCT"
  
  Idents(seurat.list[[i]]) <- "seurat_clusters"
}



# A list of cell cycle markers, from Tirosh et al, 2015, is loaded with Seurat.  
# We can segregate this list into markers of G2/M phase and markers of S phase
s.genes <- cc.genes.updated.2019$s.genes
g2m.genes <- cc.genes.updated.2019$g2m.genes


length(s.genes) # 43
length(g2m.genes) # 54

#######################
# Cell cycle analysis
#######################

seurat.list$Healthy <- CellCycleScoring(seurat.list$Healthy, 
                                       s.features = s.genes, 
                                       g2m.features = g2m.genes, 
                                       set.ident = TRUE)


#######################
# Visualisation
#######################


# Vln plots

VlnPlot(seurat.list$Healthy,
        features = "S.Score",
        group.by = "named_clusters",
        pt.size = 0)

dev.copy(pdf, "output/figures/cell_cycle/Cellcycle_VlnPlot_Sscore.pdf")
dev.off()

VlnPlot(seurat.list$Healthy,
        features = "G2M.Score",
        group.by = "named_clusters",
        pt.size = 0)

dev.copy(pdf, "output/figures/cell_cycle/Cellcycle_VlnPlot_G2Mscore.pdf")
dev.off()

```

